---
title: "Week 4 Activity, Part 2"
author: 'Group X: A, B, C, D'
date: "9/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Part 2 (ggplot2)

In this part of the activity, you will use the summary data below and attempt
to reproduce the plot in each question using ggplot.

Here is some preparatory work to get the summary results (partially) into
shape for plotting. 

```{r prep, message = FALSE}
# libraries
library(tidyverse)

# read in summary results
q2_df = readr::read_delim("./w4_p2_RECS2015_internet.csv", delim = ",")
```

```{r prep_reshape}
# reshape for plotting
plot_data = q2_df %>%
  pivot_longer(cols = starts_with('p_int'), names_prefix = 'p_int',
               names_to = 'var') %>%
  mutate( rurality = stringr::str_replace_all(var, '_.*', ''),
          type = ifelse( grepl('_', var), 
                        stringr::str_replace_all(var, '.*_', ''),
                        'est'
                        )
  ) %>%
  pivot_wider(id_cols = c('division', 'rurality'), 
              names_from = type, 
              values_from = value
  ) 
```

1. Write code where indicated to match the first figure included in the README.
```{r q1_fig1, fig.cap = cap, message = FALSE}
plot_data %>% filter(rurality != "diff") %>%
  ggplot(aes(y = division, x = est, xmin = lwr, xmax = upr, group = rurality, color = rurality))+
  geom_errorbarh( 
    aes(xmin = lwr, xmax = upr),
    position = position_dodge(width = 0.5),
    height = 0.75,
    alpha = 0.75
   ) +
   geom_point(
     position = position_dodge2(width = 0.5)
   ) +
  theme_minimal()+
    labs(x = "proportion of homes with internet access")


# Remove comments to plot and save
#ggsave(p1, 'w4_p2_q1_plot.png')
#p1
```

2. Write code where indicated to match the second figure included in the README.
```{r q2_fig2, fig.cap = cap, message = FALSE}
plot_data %>% filter(rurality == "diff") %>%
  ggplot(aes(y = division, x = est, xmin = lwr, xmax = upr)) +
  geom_errorbarh() +
  geom_point() +
  theme_minimal() +
  geom_vline(xintercept = 0, lty = 2) +
  labs(x = "Difference in proportion of homes with internet access")
```

